Neuroecon Poster Figures

### 2017-10-03 code/Lit_Review_Figure.Rmd
added references page with the interactive plot link

Interactive plot - not rendered for now

```{r warning=FALSE, message=FALSE, fig.height=36, echo=FALSE, eval=FALSE}
ggplotly(fig_data %>%
  mutate(dv = factor(dv, levels = dv[order(task)]),
         days_cutoff = ifelse(days < 60, days, 120),
         days = paste(days, '; reference:', reference)) %>%
ggplot(aes(x = dv, y = retest_reliability, label=days))+
  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
  coord_flip()+
  theme_bw()+
  theme(legend.position="none"),
tooltip = c('sample_size', 'type', 'dv', 'retest_reliability', 'days')) %>%
  layout(showlegend=FALSE)
```

>>>>

References mentioned in the plot below can be found [here](https://docs.google.com/spreadsheets/d/1hcED4_rWSGSE8Td0aqT0kWqlLCBAzRNKBXj3tSram58/edit?usp=sharing).

Interactive plot

```{r warning=FALSE, message=FALSE, fig.height=36, echo=FALSE}
ggplotly(fig_data %>%
  mutate(dv = factor(dv, levels = dv[order(task)]),
         days_cutoff = ifelse(days < 60, days, 120),
         days = paste(days, '; reference:', reference)) %>%
ggplot(aes(x = dv, y = retest_reliability, label=days))+
  geom_point(aes(color = task, size=sample_size, shape = type, alpha = days_cutoff))+
  coord_flip()+
  theme_bw()+
  theme(legend.position="none"),
tooltip = c('sample_size', 'type', 'dv', 'retest_reliability', 'days')) %>%
  layout(showlegend=FALSE)
```

### 2017-10-03 code/NeuroeconPoster.Rmd
added references page with the interactive plot link

```{r warning=FALSE, message=FALSE}
lit_rev_uniq_dvs = fig_data %>%
  distinct(dv, .keep_all=T) %>%
  select(-retest_reliability, -type, -days, -sample_size, -reference, -measure_description, -task)

boot_df_lit_rev = boot_df %>%
  left_join(lit_rev_uniq_dvs, by = "dv") %>%
  na.omit()

p4 <- boot_df_lit_rev %>%
  filter(task == 'task') %>%
ggplot(aes(y = var, x = icc)) + 
  geom_point(color = '#00BFC4')+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.75, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180, size=20),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80")) + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 17, 3))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p5 <- boot_df_lit_rev %>%
  filter(task == 'survey') %>%
ggplot(aes(y = var, x = icc)) + 
  geom_point(color = '#F8766D')+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.75, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180, size=20),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80")) + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 17, 3))+
  geom_vline(xintercept = 0, color = "red", size = 1)

>>>>

```{r warning=FALSE, message=FALSE}
boot_df_poster = boot_df[boot_df$dv %in% poster_vars$var,]

boot_df_poster = boot_df_poster%>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var)) %>%
  arrange(task_group, var)

boot_df_poster = boot_df_poster %>%
  left_join(rel_df[,c("dv", "icc")], by = "dv") %>%
  rename(icc = icc.x, point_est = icc.y)
```

```{r warning=FALSE, message=FALSE} 
p4 <- boot_df_poster %>%
  filter(task == 'task') %>%
ggplot(aes(y = var, x = icc)) + 
  geom_point(color = '#00BFC4')+
  geom_point(aes(y = var, x = point_est), color = "black")+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.75, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180, size=20),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80")) + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 17, 3))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p5 <- boot_df_poster %>%
  filter(task == 'survey') %>%
ggplot(aes(y = var, x = icc)) + 
  geom_point(color = '#F8766D')+
  geom_point(aes(y = var, x = point_est), color = "black")+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.75, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180, size=20),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80")) + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 17, 3))+
  geom_vline(xintercept = 0, color = "red", size = 1)
